noam_final_analyses

### 2024-09-05 noam_final_analyses.Rmd
added synchrony diversity stability models at the site level for all algae and just macroalgae. Added figures as well.

>>>>

```{r synchrony diversity stability setup site level, fig.height = 8, fig.width= 8}

lm_synchrony_site <- codyn::synchrony(df = site_long_data,
                                   time.var = "year",
                                   species.var = "taxa",
                                   abundance.var = "percent_cover",
                                   metric = "Loreau",
                                   replicate.var = "site_habitat") 
colnames(lm_synchrony_site) = c("site_habitat", "loreau_synchrony") # rename cols for merge later

lm_synchrony_site_macro <- codyn::synchrony(df = site_long_macro,
                                   time.var = "year",
                                   species.var = "taxa",
                                   abundance.var = "percent_cover",
                                   metric = "Loreau",
                                   replicate.var = "site_habitat") 
colnames(lm_synchrony_site_macro) = c("site_habitat", "loreau_synchrony") # rename cols for merge later

diversity_cv_site <- alpha_diversity_site %>%
  dplyr::group_by(site, habitat, island_side, site_habitat) %>%
  dplyr::summarise(
            algae_richness_mean = mean(richness), 
            algae_richness_cv = CV(richness),
            algae_richness_stability = 1/CV(richness),
            algae_shannon_mean = mean(shannon), 
            algae_shannon_cv = CV(shannon),
            algae_shannon_stability = 1/CV(shannon), 
            algae_cover_mean = mean(all_algae_cover_hard),
            algae_cover_cv = CV(all_algae_cover_hard),
            algae_cover_stability = 1/CV(all_algae_cover_hard)) 
# an extra outer_10 was introduced for every site for some reason that is all NAs
# remove NAs and merge with synchrony
diversity_stability_site <- merge(lm_synchrony_site, na.omit(diversity_cv_site), by = "site_habitat")

diversity_cv_site_macro <- alpha_diversity_site_macro %>%
  dplyr::group_by(site, habitat, island_side, site_habitat) %>%
  dplyr::summarise(
            algae_richness_mean = mean(richness), 
            algae_richness_cv = CV(richness),
            algae_richness_stability = 1/CV(richness),
            algae_shannon_mean = mean(shannon), 
            algae_shannon_cv = CV(shannon),
            algae_shannon_stability = 1/CV(shannon), 
            algae_cover_mean = mean(macroalgae_cover_hard),
            algae_cover_cv = CV(macroalgae_cover_hard),
            algae_cover_stability = 1/CV(macroalgae_cover_hard)) 
# an extra outer_10 was introduced for every site for some reason that is all NAs
# remove NAs and merge with synchrony
diversity_stability_site_macro <- merge(lm_synchrony_site_macro, na.omit(diversity_cv_site_macro), by = "site_habitat")

# for plotting later
diversity_ranges_site <- diversity_stability_site %>%
  group_by(habitat) %>%
  summarise(min_richness = min(algae_richness_mean),
            max_richness = max(algae_richness_mean),
            min_shannon = min(algae_shannon_mean),
            max_shannon = max(algae_shannon_mean),
            min_loreau = min(loreau_synchrony),
            max_loreau = max(loreau_synchrony))

diversity_ranges_site_macro <- diversity_stability_site_macro %>%
  group_by(habitat) %>%
  summarise(min_richness = min(algae_richness_mean),
            max_richness = max(algae_richness_mean),
            min_shannon = min(algae_shannon_mean),
            max_shannon = max(algae_shannon_mean),
            min_loreau = min(loreau_synchrony),
            max_loreau = max(loreau_synchrony))

```{r site all diversity stability synchrony, fig.height = 8, fig.width=8}
richness_cv_site <- glmmTMB(algae_cover_cv ~ algae_richness_mean*habitat, family = Gamma(link = "log"),
                          data = diversity_stability_site)
r.squaredGLMM(richness_cv_site) # 0.49
summary(richness_cv_site)
hist(residuals(richness_cv_site)) # symmetrical
plot(residuals(richness_cv_site) ~ fitted(richness_cv_site)) # slightly heteroskedastic
Anova(richness_cv_site)
#                               Chisq Df Pr(>Chisq)   
# algae_richness_mean          5.9078  1   0.015074 * 
# habitat                     14.5560  3   0.002238 **
# algae_richness_mean:habitat  3.8220  3   0.281336

emtrends(richness_cv_site, pairwise ~ habitat, var = "algae_richness_mean") # no significant differences
richness_cv_emm_site <- emmip(richness_cv_site,
                        habitat ~ algae_richness_mean,
                        at = list(algae_richness_mean = seq(0,10,0.1)), plotit = F, CIs = T)

filtered_richness_effects_site <- richness_cv_emm_site %>%
  left_join(diversity_ranges_site, by = c("habitat")) %>%
  filter(algae_richness_mean >= min_richness & algae_richness_mean <= max_richness)

(richness_cv_plot = 
  ggplot() +
  geom_point(data = diversity_stability_site,
             aes(x = algae_richness_mean, y = algae_cover_cv, colour = habitat), size = 2, alpha = 0.5) + 
  geom_line(data = filtered_richness_effects_site, aes(x = algae_richness_mean, y = exp(yvar), colour = habitat), size = 2) +
  geom_ribbon(data = filtered_richness_effects_site, aes(x = algae_richness_mean, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
   scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

## REPEAT WITH SHANNON
shannon_cv_site <- glmmTMB(algae_cover_cv ~ algae_shannon_mean*habitat, family = Gamma(link = "log"),
                          data = diversity_stability_site)
r.squaredGLMM(shannon_cv_site) # 0.42
summary(shannon_cv_site)
hist(residuals(shannon_cv_site)) # symmetrical
plot(residuals(shannon_cv_site) ~ fitted(shannon_cv_site)) # slightly heteroskedastic
Anova(shannon_cv_site)
#                              Chisq Df Pr(>Chisq)   
# algae_shannon_mean          1.5291  1   0.216254   
# habitat                    12.1017  3   0.007043 **
# algae_shannon_mean:habitat  2.8675  3   0.412512

emtrends(shannon_cv_site, pairwise ~ habitat, var = "algae_shannon_mean") # no significant differences
shannon_cv_emm_site <- emmip(shannon_cv_site,
                        habitat ~ algae_shannon_mean,
                        at = list(algae_shannon_mean = seq(0,10,0.1)), plotit = F, CIs = T)

filtered_shannon_effects_site <- shannon_cv_emm_site %>%
  left_join(diversity_ranges_site, by = c("habitat")) %>%
  filter(algae_shannon_mean >= min_shannon & algae_shannon_mean <= max_shannon)

(shannon_cv_plot = 
  ggplot() +
  geom_point(data = diversity_stability_site,
             aes(x = algae_shannon_mean, y = algae_cover_cv, colour = habitat), size = 2, alpha = 0.5) + 
  geom_line(data = filtered_shannon_effects_site, aes(x = algae_shannon_mean, y = exp(yvar), colour = habitat), size = 2) +
  geom_ribbon(data = filtered_shannon_effects_site, aes(x = algae_shannon_mean, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
   scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

synchrony_cv_site <- glmmTMB(algae_cover_cv ~ loreau_synchrony*habitat, family = Gamma(link = "log"),
                          data = diversity_stability_site)
r.squaredGLMM(synchrony_cv_site) # 0.76
summary(synchrony_cv_site)
hist(residuals(synchrony_cv_site)) # symmetrical
plot(residuals(synchrony_cv_site) ~ fitted(synchrony_cv_site)) # slightly heteroskedastic
Anova(synchrony_cv_site)
#                           Chisq Df Pr(>Chisq)    
# loreau_synchrony         45.857  1  1.272e-11 ***
# habitat                  14.018  3    0.00288 ** 
# loreau_synchrony:habitat  2.456  3    0.48330

emtrends(synchrony_cv_site, pairwise ~ habitat, var = "loreau_synchrony") # no differences between habitats
synchrony_cv_emm_site <- emmip(synchrony_cv_site,
                        habitat ~ loreau_synchrony,
                        at = list(loreau_synchrony = seq(0,1,0.01)), plotit = F, CIs = T)

filtered_synchrony_cv_effects_site <- synchrony_cv_emm_site %>%
  left_join(diversity_ranges_site, by = c("habitat")) %>%
  filter(loreau_synchrony >= min_loreau & loreau_synchrony <= max_loreau)

(synchrony_cv_plot = 
  ggplot() +
  geom_point(data = diversity_stability_site,
             aes(x = loreau_synchrony, y = algae_cover_cv, colour = habitat), size = 2, alpha = 0.5) + 
  geom_line(data = filtered_synchrony_cv_effects_site, aes(x = loreau_synchrony, y = exp(yvar), colour = habitat), size = 2) +
  geom_ribbon(data = filtered_synchrony_cv_effects_site, aes(x = loreau_synchrony, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
   scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

synchrony_richness_site <- glmmTMB(loreau_synchrony  ~ algae_richness_mean*habitat, family = beta_family(link = "logit"),
                          data = diversity_stability_site)
# r.squaredLR(synchrony_richness_site)
summary(synchrony_richness_site)
hist(residuals(synchrony_richness_site)) # symmetrical
plot(residuals(synchrony_richness_site) ~ fitted(synchrony_richness_site)) # slightly heteroskedastic
Anova(synchrony_richness_site)
# 
#                               Chisq Df Pr(>Chisq)    
# algae_richness_mean         12.6670  1  0.0003722 ***
# habitat                      5.0218  3  0.1702104    
# algae_richness_mean:habitat  6.0890  3  0.1073579

emtrends(synchrony_richness_site, pairwise ~ habitat, var = "algae_richness_mean") # no differences between habitats
synchrony_richness_emm_site <- emmip(synchrony_richness_site,
                        habitat ~ algae_richness_mean,
                        at = list(algae_richness_mean = seq(0,10,0.1)), plotit = F, CIs = T)

filtered_synchrony_richness_effects_site <- synchrony_richness_emm_site %>%
  left_join(diversity_ranges_site, by = c("habitat")) %>%
  filter(algae_richness_mean >= min_richness & algae_richness_mean <= max_richness)

(synchrony_richness_plot = 
  ggplot() +
  geom_point(data = diversity_stability_site,
             aes(x = algae_richness_mean, y = loreau_synchrony, colour = habitat), size = 2, alpha = 0.5) + 
  geom_line(data = filtered_synchrony_richness_effects_site, aes(x = algae_richness_mean, y = exp(yvar), colour = habitat), size = 2) +
  geom_ribbon(data = filtered_synchrony_richness_effects_site, aes(x = algae_richness_mean, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
   scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

synchrony_shannon_site <- glmmTMB(loreau_synchrony  ~ algae_shannon_mean*habitat, family = beta_family(link = "logit"),
                          data = diversity_stability_site)
# r.squaredLR(synchrony_shannon_site)
summary(synchrony_shannon_site)
hist(residuals(synchrony_shannon_site)) # symmetrical
plot(residuals(synchrony_shannon_site) ~ fitted(synchrony_shannon_site)) # slightly heteroskedastic
Anova(synchrony_shannon_site)
# 
#                              Chisq Df Pr(>Chisq)   
# algae_shannon_mean         10.5506  1   0.001161 **
# habitat                     4.9410  3   0.176171   
# algae_shannon_mean:habitat  6.1573  3   0.104205

emtrends(synchrony_shannon_site, pairwise ~ habitat, var = "algae_shannon_mean") # no differences between habitats
synchrony_shannon_emm_site <- emmip(synchrony_shannon_site,
                        habitat ~ algae_shannon_mean,
                        at = list(algae_shannon_mean = seq(0,1.5,0.01)), plotit = F, CIs = T)

filtered_synchrony_shannon_effects_site <- synchrony_shannon_emm_site %>%
  left_join(diversity_ranges_site, by = c("habitat")) %>%
  filter(algae_shannon_mean >= min_shannon & algae_shannon_mean <= max_shannon)

(synchrony_shannon_plot = 
  ggplot() +
  geom_point(data = diversity_stability_site,
             aes(x = algae_shannon_mean, y = loreau_synchrony, colour = habitat), size = 2, alpha = 0.5) + 
  geom_line(data = filtered_synchrony_shannon_effects_site, aes(x = algae_shannon_mean, y = exp(yvar), colour = habitat), size = 2) +
  geom_ribbon(data = filtered_synchrony_shannon_effects_site, aes(x = algae_shannon_mean, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
   scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

```{r site macroalgae diversity stability synchrony, fig.height = 8, fig.width=8}
richness_cv_site_macro <- glmmTMB(algae_cover_cv ~ algae_richness_mean*habitat, family = Gamma(link = "log"),
                          data = diversity_stability_site_macro)
r.squaredGLMM(richness_cv_site_macro) # 0.65
summary(richness_cv_site_macro)
hist(residuals(richness_cv_site_macro)) # symmetrical
plot(residuals(richness_cv_site_macro) ~ fitted(richness_cv_site_macro)) # not bad
Anova(richness_cv_site_macro)
#                               Chisq Df Pr(>Chisq)   
# algae_richness_mean         15.772  1  7.144e-05 ***
# habitat                     21.689  3  7.572e-05 ***
# algae_richness_mean:habitat 12.244  3   0.006591 **

emtrends(richness_cv_site_macro, pairwise ~ habitat, var = "algae_richness_mean") # backreef differs from two forereef sites
richness_cv_emm_site_macro <- emmip(richness_cv_site_macro,
                        habitat ~ algae_richness_mean,
                        at = list(algae_richness_mean = seq(0,10,0.1)), plotit = F, CIs = T)

filtered_richness_effects_site_macro <- richness_cv_emm_site_macro %>%
  left_join(diversity_ranges_site_macro, by = c("habitat")) %>%
  filter(algae_richness_mean >= min_richness & algae_richness_mean <= max_richness)

(richness_cv_plot = 
  ggplot() +
  geom_point(data = diversity_stability_site_macro,
             aes(x = algae_richness_mean, y = algae_cover_cv, colour = habitat), size = 2, alpha = 0.5) + 
  geom_line(data = filtered_richness_effects_site_macro, aes(x = algae_richness_mean, y = exp(yvar), colour = habitat), size = 2) +
  geom_ribbon(data = filtered_richness_effects_site_macro, aes(x = algae_richness_mean, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
   scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

## REPEAT WITH SHANNON
shannon_cv_site_macro <- glmmTMB(algae_cover_cv ~ algae_shannon_mean*habitat, family = Gamma(link = "log"),
                          data = diversity_stability_site_macro)
r.squaredGLMM(shannon_cv_site_macro) # 0.37
summary(shannon_cv_site_macro)
hist(residuals(shannon_cv_site_macro)) # a little chunky
plot(residuals(shannon_cv_site_macro) ~ fitted(shannon_cv_site_macro)) # pretty good
Anova(shannon_cv_site_macro)
#                             Chisq Df Pr(>Chisq)  
# algae_shannon_mean         1.1533  1    0.28287  
# habitat                    7.9691  3    0.04666 *
# algae_shannon_mean:habitat 4.1867  3    0.24199

emtrends(shannon_cv_site_macro, pairwise ~ habitat, var = "algae_shannon_mean") # no significant differences
shannon_cv_emm_site_macro <- emmip(shannon_cv_site_macro,
                        habitat ~ algae_shannon_mean,
                        at = list(algae_shannon_mean = seq(0,2,0.01)), plotit = F, CIs = T)

filtered_shannon_effects_site_macro <- shannon_cv_emm_site_macro %>%
  left_join(diversity_ranges_site_macro, by = c("habitat")) %>%
  filter(algae_shannon_mean >= min_shannon & algae_shannon_mean <= max_shannon)

(shannon_cv_plot = 
  ggplot() +
  geom_point(data = diversity_stability_site_macro,
             aes(x = algae_shannon_mean, y = algae_cover_cv, colour = habitat), size = 2, alpha = 0.5) + 
  geom_line(data = filtered_shannon_effects_site_macro, aes(x = algae_shannon_mean, y = exp(yvar), colour = habitat), size = 2) +
  geom_ribbon(data = filtered_shannon_effects_site_macro, aes(x = algae_shannon_mean, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
   scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

synchrony_cv_site_macro <- glmmTMB(algae_cover_cv ~ loreau_synchrony*habitat, family = Gamma(link = "log"),
                          data = diversity_stability_site_macro)
r.squaredGLMM(synchrony_cv_site_macro) # 0.71
summary(synchrony_cv_site_macro)
hist(residuals(synchrony_cv_site_macro)) # symmetrical
plot(residuals(synchrony_cv_site_macro) ~ fitted(synchrony_cv_site_macro)) # slightly heteroskedastic
Anova(synchrony_cv_site_macro)
#                           Chisq Df Pr(>Chisq)    
# loreau_synchrony         22.575  1  2.021e-06 ***
# habitat                  11.611  3   0.008841 ** 
# loreau_synchrony:habitat 11.389  3   0.009799 **

emtrends(synchrony_cv_site_macro, pairwise ~ habitat, var = "loreau_synchrony") # backreef different from outer17
synchrony_cv_emm_site_macro <- emmip(synchrony_cv_site_macro,
                        habitat ~ loreau_synchrony,
                        at = list(loreau_synchrony = seq(0,1,0.01)), plotit = F, CIs = T)

filtered_synchrony_cv_effects_site_macro <- synchrony_cv_emm_site_macro %>%
  left_join(diversity_ranges_site_macro, by = c("habitat")) %>%
  filter(loreau_synchrony >= min_loreau & loreau_synchrony <= max_loreau)

(synchrony_cv_plot = 
  ggplot() +
  geom_point(data = diversity_stability_site_macro,
             aes(x = loreau_synchrony, y = algae_cover_cv, colour = habitat), size = 2, alpha = 0.5) + 
  geom_line(data = filtered_synchrony_cv_effects_site_macro, aes(x = loreau_synchrony, y = exp(yvar), colour = habitat), size = 2) +
  geom_ribbon(data = filtered_synchrony_cv_effects_site_macro, aes(x = loreau_synchrony, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
   scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

synchrony_richness_site_macro <- glmmTMB(loreau_synchrony  ~ algae_richness_mean*habitat, family = beta_family(link = "logit"),
                          data = diversity_stability_site_macro)
# r.squaredGLMM(synchrony_richness_site_macro)
summary(synchrony_richness_site_macro)
hist(residuals(synchrony_richness_site_macro)) # kind of chunky
plot(residuals(synchrony_richness_site_macro) ~ fitted(synchrony_richness_site_macro)) # slightly heteroskedastic
Anova(synchrony_richness_site_macro)
# 
#                               Chisq Df Pr(>Chisq)    
# algae_richness_mean         0.2299  1    0.63161  
# habitat                     5.4261  3    0.14312  
# algae_richness_mean:habitat 9.1650  3    0.02718 *

emtrends(synchrony_richness_site_macro, pairwise ~ habitat, var = "algae_richness_mean") # backreef almost diff from fing and outer17
synchrony_richness_emm_site_macro <- emmip(synchrony_richness_site_macro,
                        habitat ~ algae_richness_mean,
                        at = list(algae_richness_mean = seq(0,10,0.1)), plotit = F, CIs = T)

filtered_synchrony_richness_effects_site_macro <- synchrony_richness_emm_site_macro %>%
  left_join(diversity_ranges_site_macro, by = c("habitat")) %>%
  filter(algae_richness_mean >= min_richness & algae_richness_mean <= max_richness)

(synchrony_richness_plot = 
  ggplot() +
  geom_point(data = diversity_stability_site_macro,
             aes(x = algae_richness_mean, y = loreau_synchrony, colour = habitat), size = 2, alpha = 0.5) + 
  geom_line(data = filtered_synchrony_richness_effects_site_macro, aes(x = algae_richness_mean, y = exp(yvar), colour = habitat), size = 2) +
  geom_ribbon(data = filtered_synchrony_richness_effects_site_macro, aes(x = algae_richness_mean, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
   scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

synchrony_shannon_site_macro <- glmmTMB(loreau_synchrony  ~ algae_shannon_mean*habitat, family = beta_family(link = "logit"),
                          data = diversity_stability_site_macro)
summary(synchrony_shannon_site_macro)
hist(residuals(synchrony_shannon_site_macro)) # a little chunky
plot(residuals(synchrony_shannon_site_macro) ~ fitted(synchrony_shannon_site_macro)) # slightly heteroskedastic
Anova(synchrony_shannon_site_macro)
# 
#                              Chisq Df Pr(>Chisq)   
# algae_richness_mean         0.2299  1    0.63161  
# habitat                     5.4261  3    0.14312  
# algae_richness_mean:habitat 9.1650  3    0.02718 *

emtrends(synchrony_shannon_site_macro, pairwise ~ habitat, var = "algae_shannon_mean") # no differences between habitats
synchrony_shannon_emm_site_macro <- emmip(synchrony_shannon_site_macro,
                        habitat ~ algae_shannon_mean,
                        at = list(algae_shannon_mean = seq(0,1.5,0.01)), plotit = F, CIs = T)

filtered_synchrony_shannon_effects_site_macro <- synchrony_shannon_emm_site_macro %>%
  left_join(diversity_ranges_site_macro, by = c("habitat")) %>%
  filter(algae_shannon_mean >= min_shannon & algae_shannon_mean <= max_shannon)

(synchrony_shannon_plot = 
  ggplot() +
  geom_point(data = diversity_stability_site_macro,
             aes(x = algae_shannon_mean, y = loreau_synchrony, colour = habitat), size = 2, alpha = 0.5) + 
  geom_line(data = filtered_synchrony_shannon_effects_site_macro, aes(x = algae_shannon_mean, y = exp(yvar), colour = habitat), size = 2) +
  geom_ribbon(data = filtered_synchrony_shannon_effects_site_macro, aes(x = algae_shannon_mean, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
   scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )
